---
title: "Generate Questions for MyLearn"
output:
  md_document:
    variant: markdown_github
  pdf_document: default
author: Darjus Hosszejni, WU Vienna
---

Question Generation for MyLearn
===============================

Randomized multiple-select and single-select question generation for the MyLearn platform at the Vienna University of Economics and Business.
Question templates in the form of the [R/exams](http://www.r-exams.org/) package are transformed into MyLearn's XML format.
Note that the feedback has to stay simple.
The imported questions can be organized into exams in the Learning Activities.

Dependencies:

* libxml2 (it was on my Ubuntu by default)
* pandoc
* recent `R` version and popular `R` packages

The question import functionality has to be turned on by the Learn development team per course.
Their address is "learn" `at` "wu" `dot` "ac" `dot` "at".

Installation
------------

```{r, echo=TRUE, eval=FALSE}
install.packages("devtools")
devtools::install_github("https://github.com/hdarjus/WU-MyLearn-QGen")
```

Demo
----

One creates an `R/exams` compatible exercise file similar to `example_question.Rmd`, decides for a name prefix and for the number of generated exams.

```{r, echo=TRUE, eval=FALSE}
library("exams.wuvienna")
n <- 100L  # number of variants of the exercise
name <- "learn_exercise"  # prefix of the generated file names
exercise_file <- example_paths()["R_table"]
output <- exams2mylearn(filename = exercise_file,
                        name = name,
                        n = n)
```

The output zip filepath is saved in `output`.
One can upload that zip file to Learn directly (after the Learn development team has activated that feature for the given course).

I have tested the framework with the examples returned by `example_paths()`.
I managed to upload 100 questions to Learn at the same time and then import them in a Poolfolder, so it seems to work.

Further Reading
---------------

For how to import the generated questions, please contact the learn team.

For how you could use the imported questions, please read up on Poolfolders and Proxy questions, Sample Exams, Strict Sequencing Study Modules in the MyLearn-Guide.

Maintainance
----------

Should you find bugs, please use the [Issue tracker on Github](https://github.com/hdarjus/WU-MyLearn-QGen/issues).
If you have a minimal example of a .Rmd question that does not compile or Learn gives an error at the stage of import, you can contact me under "darjus" `dot` "hosszejni" `at` "wu" `dot` "ac" `dot` "at".
Please attach the .Rmd file in question.
